Data Preparation

### 2019-01-14 Data Preparation.Rmd

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)
rm(stem_hunspell, stem_with_dictionary)
print(d_overview) # See humanities - humanity
```

### Removing Stopwords
Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________")
remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))
d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)
rm(sw_own, remove_sw)
```

>>>>

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)
rm(stem_hunspell, stem_with_dictionary)
print(d_description) # See starting - start
```

### Removing Stopwords
Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________")
remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))
d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)

rm(sw_own, remove_sw)
print(d_description) # stop words (on, the, of, etc, are excluded)
```
